Longitudinal Analysis of the Privacy Calculus

### 2020-04-23 analyses.Rmd
setting up github website

---
title: "A Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
editor_options: 
  chunk_output_type: inline
---

```{r, echo=F, include=F}
# defaults
set.seed(170819)
options(digits=3, width=120, max.print=100000)
knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=F)
```

```{r Packages, include=F, cache=F}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

# export bib library
r_refs("../bibliography/r-references.bib")
```

```{r datawrangling, include=F}
# first run "data_wranling.R", in order to create these objects
d_wide <- read_csv("../data/data_wide.csv")
d_wide_all <- read_csv("../data/data_wide_all.csv")
d_long <- read_csv("../data/data_long.csv")
```

```{r include=F}
# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```

@@

```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
knitr::include_graphics("../figures/model_7.png")
```

@@

```{r cache=F}
save.image("../data/workspace.RData")
```

>>>>

---
title: "A Longitudinal Analysis of the Privacy Paradox"
author: "Tobias Dienlin, Philipp K. Masur, Sabine Trepte"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
    code_folding: hide
---

```{r, echo=F, include=F}
# defaults
set.seed(170819)
options(digits=3, width=120, max.print=100000)
knitr::opts_chunk$set(echo=T, error=F, message=F, tidy=T, warning=F, cache=T)
```

```{r Packages, cache=F, results='hide'}
# relevant packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
required <- c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
              "MissMech", "papaja", "psych", "pwr", "MVN", "semTools", 
              "sjstats", "tidyverse", "td")

@@

# export bib library
r_refs("bibliography/r-references.bib")

# first run "data_wranling.R", in order to create these objects
d_wide <- read_csv("data/data_wide.csv")
d_wide_all <- read_csv("data/data_wide_all.csv")
d_long <- read_csv("data/data_long.csv")

# Extract descriptives to report in paper
desc <- d_wide %>% 
  summarize_at(vars(ends_with("_m")), funs(mean(., na.rm = TRUE), sd(., na.rm = TRUE)))
```

@@

```{r, fig.cap="Visual representation of the estimated random-intercept cross-lagged panel model (RI-CLPM)."}
knitr::include_graphics("figures/model_7.png")
```

@@

```{r cache=F}
save.image("data/workspace.RData")
```

### 2020-04-23 manuscript.RmD
setting up github website

  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [../bibliography/references.bib]
  - [../bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
editor_options: 
  chunk_output_type: inline
---
```{r knitr-set-up}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

```{r load-packs, include = F}
# Load and install packages
devtools::install_github("tdienlin/td@v.0.0.2.5")
devtools::install_github("crsh/papaja")
packages <- c("broman", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
             , "psych", "pwr", "td", "tidyverse", "semTools", "scales")
invisible(lapply(packages, library, character.only = T))

# load r-bib
r_citations <- cite_r("../bibliography/r-references.bib", 
                      footnote = FALSE, 
                      pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
                               "MissMech", "MVN", "papaja", "psych", "pwr",  
                               "semTools", "sjstats", "tidyverse", "td"), 
                      withhold = FALSE)
```

```{r load-data, include=F, cache=T}
# Load Workspace
load("../data/workspace.RData")
```

>>>>

  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [bibliography/references.bib]
  - [bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
# to compile as pdf
# (a) move file "_site.yml" to folder "tmp"
# (b) uncomment the following lines; comment lines after "output: html_document ..."
# output            : papaja::apa6_pdf
# header-includes:
#   - \setlength{\parskip}{0em}
#   - \raggedbottom
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

```{r knitr-set-up, include=F}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

```{r load-packs, include=F}
# Load and install packages
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncommen to install
packages <- c("broman", "kableExtra", "knitr", "lavaan", "magrittr", "papaja"
             , "psych", "pwr", "td", "tidyverse", "semTools", "scales")
invisible(lapply(packages, library, character.only = T))

# load r-bib
r_citations <- cite_r("bibliography/r-references.bib", 
                      footnote = FALSE, 
                      pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
                               "MissMech", "MVN", "papaja", "psych", "pwr",  
                               "semTools", "sjstats", "tidyverse", "td"), 
                      withhold = FALSE)
```

```{r load-data, include=F, cache=T}
# Load Workspace
load("data/workspace.RData")
```

# Introduction
